---
title: "Sole 27.4 - 2021 forecast"
subtitle: "ICES WGNSSK. Web, 21-30 April 2021"
author: Iago MOSQUEIRA
institute: Wageningen Marine Research (WMR), IJmuiden, The Netherlands.
fontsize: 10pt
output:
  wmrkdown::wur:
    slide_level: 1
header-includes:
  - \newcommand{\fig}[2][0.70]{\centering\includegraphics[width=#1\textwidth]{../report/#2}}
custom: images/beamtrawl.jpg
tags: [sol.27.4 SA]
---

```{r, knitr, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE,
  fig.width=5, fig.height=3, fig.pos='H', fig.align='center')
library(kableExtra)
library(ggplotFL)
library(icesAdvice)
library(AAP)
```

```{r data}
load('../output/aap.RData', verbose=FALSE)
load("../model/runs.RData", verbose=FALSE)
load('../output/tables.RData', verbose=FALSE)
dy <- dims(run)$maxyear
ay <- dy + 1
fy <- ay + 1
```

# AAP 2020 assessment

```{r, out.height="90%", fig.height=7}
plot(fit)
```

# Forecast assumptions and settings

- Natural mortality: 0.1 / year.
- Maturity: kinfe-edge at age 3.
- F and M before spawning: 0
- Weights at age catch & stock: 5 year average.
- Selectivity at age: 5 year average.
- Discards ratio at age: 3 year average.

```{r fbar, out.width="60%"}
plot(window(fbar(run), start=2000)) + ylim(c(0, NA)) +
  geom_point(size=1.2, color="black") + geom_point(size=0.7, color="white") +
  ylab("F (2-6)") + xlab("")
```

# Intermediate year assumptions

- TAC 2020: 17,545 t
- Catch `r dy`: `r formatC(c(catch(run)[, ac(dy)]), format="f", big.mark=",", digits=0)` t
- TAC 2021: 21,361 t
- Catch 2021 (F 2020=0.23) = 16,656 t
- F 2021 = 0.23
- Recruitment: Geometric mean 1957-2017

# Reference points

```{r ssbandf,  fig.width=12, fig.height=5, out.width="95%", dpi=250}
(plot(fbar(fit)) +
  geom_hline(yintercept=c(refpts$Flim), color="red", size=0.25)+
    geom_text(x=ISOdate(1957,1,1), y=c(refpts$Flim + 0.02), label=expression(F[lim])) +
  geom_hline(yintercept=c(refpts$F05), linetype=3) +
    geom_text(x=ISOdate(1957,1,1), y=c(refpts$F05 + 0.02), label=expression(F[PA])) +
  geom_hline(yintercept=c(refpts$Fmsy), linetype=2) +
    geom_text(x=ISOdate(1957,1,1), y=c(refpts$Fmsy + 0.02), label=expression(F[MSY])) +
  ylim(c(0,NA)) + ylab("F (ages 2-6)")) +

(plot(ssb(fit)) +
  geom_hline(yintercept=c(refpts$Bpa), color="red", size=0.25) +
    geom_text(x=ISOdate(1957,1,1), y=c(refpts$Bpa - 2500), label=expression(B[PA]),
     hjust="inward") +
  geom_hline(yintercept=c(refpts$Btrigger), linetype=3) +
    geom_text(x=ISOdate(1957,1,1), y=c(refpts$Btrigger + 2000),
       label=expression(MSYB[trigger]), hjust="inward") +
  geom_hline(yintercept=c(refpts$Blim), linetype=2) +
    geom_text(x=ISOdate(1957,1,1), y=c(refpts$Blim + 2000), label=expression(B[lim]), hjust="inward") +
  ylim(c(0,NA)) + ylab("SSB (tonnes)"))
```

```{r refpts}
dat <- as.data.frame(refpts, drop=TRUE)
dat[, 'data'] <- icesRound(dat[, 'data'])
colnames(dat) <- c("", "")

d <- as.data.frame(t(dat[1:8,]))
rownames(d) <- NULL
colnames(d) <- NULL

kable_styling(
kable(d, format.args = list(big.mark = ",")),
  position = "center")
```

# Catch options

\Tiny

```{r}

cnames <- c(basis="Basis", catch="Catch", wanted="Wanted",
    unwanted="Unwanted", F="F(2-6)",
    Fwanted="Wanted", Funwanted= "Unwanted", 
    SSB="SSB (2022)", ssbchange="%SSB", tacchange="%TAC",
    advicechange="%Advice")

colnames(tab_options) <- cnames

add_header_above(kable(tab_options), c(" ", "(2022)"=3, "(2022)"=3, "(2023)",
  "(2023/2022)", "(2022/2021)"=2))
```

# Stock projection

```{r fig.width=8, fig.height=6, out.width="85%", dpi=250}

mets <- metrics(runs$Fmsy)

mets$F[,'2023'] <- NA
mets$Catch[,'2023'] <- NA
names(mets)[4] <- "F (age 2-6)"

plot(mets) + geom_vline(xintercept=2020, alpha=0.4) +
  geom_vline(xintercept=2022, alpha=0.2) +
  annotate("rect", xmin = 2020, xmax = 2023, ymin = -Inf, ymax = Inf,
  fill = "#FF9900", alpha=0.1)
```

# Uncertainty in SSB

\fig[0.85]{model_ssbmc.png}
